Computer Science House Constitution

### 2019-04-22 articles.tex
Differentiate Chair from chairperson of the vote
Standardises the use of 'chairperson of the vote' when referring to the
chair of a specific vote and not the Chair of House

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairman
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asubsection{Responsibilities of Ad Hoc Directorships}
\begin{enumerate}
	\item Ad-Hoc Directorships are responsible for the task for which they were created
	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
\end{enumerate}

@@

\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

\asubsection{Selection of Ad Hoc Directors}

@@

	\item When the Executive Board or a group of House members feels an Ad-hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

>>>>

% ARTICLE IV - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairman.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad-Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairman
	\item House Secretary
	\item Ad-Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asubsection{Responsibilities of Ad-Hoc Directorships}
\begin{enumerate}
	\item Ad-Hoc Directorships are responsible for the task for which they were created
	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
\end{enumerate}

@@

\asubsection{Qualifications to be the House Secretary or an Ad-Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

\asubsection{Selection of Ad-Hoc Directors}

@@

	\item When the Executive Board or a group of House members feels an Ad-Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad-Hoc Directorship has been completed, the directorship dissolves.
	When an Ad-Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}
